### 2021-12-09 Slides.Rmd
Initial slides

---
title: "A Machine Learning Approach to MLB Catcher Framing"
author: "Nathan Hemenway and Matthew Boyd"
date: "12/10/2021"
output: 
  beamer_presentation: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(gbm)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- "Catcher framing is the art of a catcher receiving a pitch in a way that makes it more likely for an umpire to call it a strike -- whether that's turning a borderline ball into a strike, or not losing a strike to a ball due to poor framing." - MLB.com Glossery

## Motivation

- Baseball Catcher's can influence the call of a ball or strike on how they catch the ball
- Some catcher's are better than others at this skill
- Baseball teams are aware of this and are acquiring players good at this skill to win more games
- We want to quantify the best catcher's at framing for the 2021 season
- There are several factors that influence whether a pitch will be a strike or ball

## Data

- 2021 pitch data scraped from Baseball Savant through baseballr package
- ~700,000 rows (each for a single pitch)
- Wanted to look at pitches that were not swung at by the batter (called strike or ball)
- ~350,000 rows remain

## Variables

- which variables used and why

## Example

- Strike Probability by Location and Count

```{r cars, echo = FALSE, message = FALSE, cache=TRUE}
load("Data/usable_data.Rda")
x=c(-0.95,0.95,0.95,-0.95,-0.95)
y=c(1.5,1.5,3.5,3.5,1.5)
sz=data.frame(x,y)
# Take some samples to explore
train = usable_data %>% slice(1000:150000) %>%
  mutate(strike = as.character(strike)) %>%
  select(-catcher_name)

# Train initial model

model = gbm(strike ~ plate_x + plate_z + count, 
                     data = train, n.trees = 200, distribution = "bernoulli")

# Create a grid of values
grid1 = data.frame()
x = seq(-1.8, 1.8, length.out = 125)
y = seq(1.2, 3.8, length.out = 125)
grid = expand.grid(plate_x = x, plate_z = y)

# This creates a new grid for every count factor to visualize
grid1 = grid1 %>% bind_rows(data.frame(grid, count = "0-0"),
                            data.frame(grid, count = "0-1"),
                            data.frame(grid, count = "0-2"),
                            data.frame(grid, count = "1-0"),
                            data.frame(grid, count = "1-1"),
                            data.frame(grid, count = "1-2"),
                            data.frame(grid, count = "2-0"),
                            data.frame(grid, count = "2-1"),
                            data.frame(grid, count = "2-2"),
                            data.frame(grid, count = "3-0"),
                            data.frame(grid, count = "3-1"),
                            data.frame(grid, count = "3-2")) %>%
  mutate(count = as.factor(count))

# Predict whether a pitch will be a strike or not
grid1 = grid1 %>%
  mutate(pred = predict(model, grid1, type = "response") >= 0.5)

# Visualize strikes by the count and location
ggplot()+
  geom_point(data = grid1, aes(x = plate_x, y = plate_z, color = pred)) +
  facet_wrap(~count) +
  geom_path(data = sz, aes(x = x, y = y)) +
  scale_color_manual(values = c("TRUE" = "red", "FALSE" = "white")) +
  labs(color = "Predicted Strike") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

### 2021-12-09 Model_Exploration.R

@@ -11,7 +11,7 @@ library(caret)
 load("Data/usable_data.Rda")
 
 
-load("Data/pitchData,Rda")
+load("Data/pitchData.Rda")
 
 # Little strike zone path for ggplot
 x=c(-0.95,0.95,0.95,-0.95,-0.95)
@@ -22,16 +22,20 @@ sz=data.frame(x,y)
 
 # Example model
 # Take some samples to explore
-train = data %>% slice(1000:50000)
+train = usable_data %>% slice(1000:150000) %>%
+  mutate(strike = as.character(strike)) %>%
+  select(-catcher_name)
 
 # Train initial model
-model = randomForest(strike ~ plate_x + plate_z + count, data = train, ntree = 1000)
+
+model = gbm(strike ~ plate_x + plate_z + count, 
+                     data = train, n.trees = 200, distribution = "bernoulli")
 
 
 # Create a grid of values
 grid1 = data.frame()
-x = seq(-2, 2, length.out = 150)
-y = seq(1, 5, length.out = 150)
+x = seq(-1.8, 1.8, length.out = 125)
+y = seq(1.2, 3.8, length.out = 125)
 grid = expand.grid(plate_x = x, plate_z = y)
 
 # This creates a new grid for every count factor to visualize
@@ -52,22 +56,19 @@ grid1 = grid1 %>% bind_rows(data.frame(grid, count = "0-0"),
 
 # Predict whether a pitch will be a strike or not
 grid1 = grid1 %>%
-  mutate(pred = predict(model, grid1))
+  mutate(pred = predict(model, grid1, type = "response") >= 0.5)
 
 # Visualize strikes by the count and location
 ggplot()+
   geom_point(data = grid1, aes(x = plate_x, y = plate_z, color = pred)) +
-  facet_wrap(~stand) +
-  geom_path(data = sz, aes(x = x, y = y))
-
-
-# Find the pitch that is called a strike with the lowest probability. Among observations we trained model on
-train$pred = predict(model, train, type = "prob")[,2]
-
-train %>% filter(strike == 1, count == "0-2") %>%
-  select(game_date.x, count, inning, catcher_name, home_team, pred) %>%
-  arrange(pred)
-
+  facet_wrap(~count) +
+  geom_path(data = sz, aes(x = x, y = y)) +
+  scale_color_manual(values = c("TRUE" = "red", "FALSE" = "white")) +
+  labs(color = "Predicted Strike") +
[…]

### 2021-12-09 Slides.Rmd
Added variables and a bit to the other intro slides

@@
 
-- "Catcher framing is the art of a catcher receiving a pitch in a way that makes it more likely for an umpire to call it a strike -- whether that's turning a borderline ball into a strike, or not losing a strike to a ball due to poor framing." - MLB.com Glossery
+- "Catcher framing is the art of a catcher receiving a pitch in a way that makes it more likely for an umpire to call it a strike -- whether that's turning a borderline ball into a strike, or not losing a strike to a ball due to poor framing." - MLB.com Glossary
 
@@
 
-- Baseball Catcher's can influence the call of a ball or strike on how they catch the ball
-- Some catcher's are better than others at this skill
+- Baseball catchers can influence the call of a ball or strike on how they catch the ball
+- Some catchers are better than others at this skill
 - Baseball teams are aware of this and are acquiring players good at this skill to win more games
@@
 - There are several factors that influence whether a pitch will be a strike or ball
+- Catchers getting more strikes translates to more outs, and fewer points for the opposing team
 
@@
 
-- which variables used and why
+- We used:
+- Pitch type and pitch release speed, position, and spin rate
+- Whether or not the pitcher and batter are right or left handed
+- Count, number of outs during the at-bat, and inning number
+- Where the pitch landed
+- Whether the game was played home or away
 

### 2021-12-09 Slides.Rmd
Added logistic regression

@@
 - Whether the game was played home or away
+- How tall the batter is
 
@@
 
-## Slide with Plot
+## Logistic Regression Model
 
-```{r pressure}
-plot(pressure)
+\tiny
+```{r, echo=FALSE}
+data_no_catchers <- usable_data[, -18]
+
+train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
+test <- (-train)
+
+log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
+summary(log_reg_fit)
+
+pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
+pred[pred >= 0.5] <- 'strike'
+pred[pred < 0.5] <- 'ball'
+sum(pred=='strike')/length(pred)
+
 ```
+
+```{r}
+conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
+error <- (conf_mx[2] + conf_mx[3])/length(pred)
+
+conf_mx
+error
+```

### 2021-12-09 Slides.Rmd
Add random forest

@@
 library(gbm)
+library(randomForest)
 knitr::opts_chunk$set(echo = FALSE)
@@
 ```
+
+## Random Forest
+
+- 3 Fold Cross Validation on Random Forest  
+  - Tested on nodesizes of 10, 30, 50, 70, 90 | 500 trees
+  - Compared Out-Of-Bag Error 
+```{r}
+load("Data/pitchData.Rda")
+load("Model-Outputs/random-forest.Rda")
+
+ggplot(df_rf, aes(x = nodesize, y = accuracy))+
+  geom_line() +
+  geom_point() +
+  geom_point(data = df_rf %>% 
+               filter(accuracy == max(accuracy)), aes(x = nodesize, y = accuracy), color = "red") +
+  ylim(0.925, 0.935) +
+  labs(x = "Nodesize",
+       y = "Accuracy",
+       title = "Random Forest OOB Accuracy by Nodesize") +
+  theme_minimal()
+```

### 2021-12-09 Trees.R

@@ -46,7 +46,13 @@ load("Model-Outputs/random-forest.Rda")
 ggplot(df_rf, aes(x = nodesize, y = accuracy))+
   geom_line() +
   geom_point() +
-  ylim(0.925, 0.935)
+  geom_point(data = df_rf %>% 
+               filter(accuracy == max(accuracy)), aes(x = nodesize, y = accuracy), color = "red") +
+  ylim(0.925, 0.935) +
+  labs(x = "Nodesize",
+       y = "Accuracy",
+       title = "Random Forest OOB Accuracy by Nodesize") +
+  theme_minimal()
 
 
 varImp(model_rf) %>% 

### 2021-12-09 Slides.Rmd
Add boosting

@@
   - Compared Out-Of-Bag Error 
-```{r}
+```{r, echo=FALSE}
 load("Data/pitchData.Rda")
@@
 ```
+
+## Boosting
+
+```{r, echo=FALSE}
+load("Model-Outputs/boosting.Rda")
+
+ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
+  geom_line() +
+  theme_minimal()+
+  geom_point() +
+  geom_point(aes(x = 16, y = 0.935), color = "red") +
+  labs(x = "Accuracy", y = "Interactin Depth",
+       color = "Shrinkage",
+       y = "Boosting Accuracy by Interaction Depth and Shrinkage")
+```

### 2021-12-09 Trees.R

@@ -108,7 +108,12 @@ load("Model-Outputs/boosting.Rda")
 
 ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
   geom_line() +
-  theme_minimal()
+  theme_minimal()+
+  geom_point() +
+  geom_point(aes(x = 16, y = 0.935), color = "red") +
+  labs(x = "Accuracy", y = "Interactin Depth (d)",
+       color = "Shrinkage",
+       y = "Boosting Accuracy by Interaction Depth and Shrinkage")
 
 
  # save(df_gbm_final, file = "Model-Outputs/boosting.Rda")

### 2021-12-09 Slides.Rmd
Boosting again

@@
 - There are several factors that influence whether a pitch will be a strike or ball
-- Catchers getting more strikes translates to more outs, and fewer points for the opposing team
+- Catchers getting more strikes translates to more outs, and fewer runs for the opposing team
 
@@
 
-- 3 Fold Cross Validation on Random Forest  
-  - Tested on nodesizes of 10, 30, 50, 70, 90 | 500 trees
+- Tested several Random Forest models
+  - Nodesize: 10, 30, 50, 70, 90 | # of Trees: 500
   - Compared Out-Of-Bag Error 
-```{r, echo=FALSE}
+```{r, echo=FALSE, fig.width=7, fig.height=3}
 load("Data/pitchData.Rda")
@@
 
-```{r, echo=FALSE}
+- 3 Fold Cross Validation on Boosting
+  - Interaction depth: 6, 11, 16 
+  - Shrinkage: 0.1, 0.01, 0.001 
+  - Number of Trees: 500
+  - Compared CV accuracy
+- 27 models took over 5 hours to run
+
+```{r, echo=FALSE, fig.width=6, fig.height=2.5}
 load("Model-Outputs/boosting.Rda")
@@
 ```
+
+## Boosting Part 2
+
+- Only tuned shrinkage and interaction depth
+- Now tune trees with interaction depth of 16 and shrinkage of 0.1
+
+```{r}
+load("Model-Outputs/boosting2.Rda")
+final_df_gbm %>%
+  group_by(trees) %>%
+  summarize(accuracy = mean(accuracy)) %>%
+  arrange(desc(accuracy)) %>%
+  ggplot(aes(x = trees, y = accuracy)) +
+  geom_line(color = "goldenrod") +
+  theme_minimal() +
+  labs(x = "Number of Trees",
+       y = "Accuracy",
+       title = "Boosting Accuracy by # of Trees")
+```

### 2021-12-09 Slides.Rmd
Boosting

@@
   - Compared Out-Of-Bag Error 
-```{r, echo=FALSE, fig.width=7, fig.height=3}
+```{r, echo=FALSE, fig.width=7, fig.height=4}
 load("Data/pitchData.Rda")
@@
        color = "Shrinkage",
-       y = "Boosting Accuracy by Interaction Depth and Shrinkage")
+       title = "Boosting Accuracy by Interaction Depth and Shrinkage")
 ```
@@
 - Now tune trees with interaction depth of 16 and shrinkage of 0.1
+- Trees: 300, 500, 600, 900, 1200
 
-```{r}
+```{r,  fig.width=6, fig.height=3.2}
 load("Model-Outputs/boosting2.Rda")

### 2021-12-10 Slides.Rmd
Added ridge regression and LASSO to slides

@@
 library(tidyverse)
+library(glmnet)
 library(gbm)
@@
 log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
-summary(log_reg_fit)
 
@@
 pred[pred < 0.5] <- 'ball'
-sum(pred=='strike')/length(pred)
 
@@
 conf_mx
-error
+1-error
 ```
+
+- The variables with significant results were:
+- Pitch type, release speed, z release position
+- Whether the batter is a lefty/righty
+- Count
+- Where the pitch landed
+- Most of the innings
+- Batter height
+- Whether it was a home game
+
+## Ridge Regression
+
+```{r}
+x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
+y <- data_no_catchers$strike
+
+lambda <- seq(0.001, 10, length=100)
+
+#Create training and test data set
+train <- sample(1:nrow(x), nrow(x)/2)
+test <- (-train)
+ridge_reg_fit <-  glmnet(x[train,], y[train], alpha = 0, lambda = lambda, family='binomial')
+
+#Choose lambda
+cv_ridge <- cv.glmnet(x[train, ], y[train], alpha=0, family='binomial')
+lambda_choice <- cv_ridge$lambda.min
+
+#Get predictions
+ridge_predict <- predict(ridge_reg_fit, s = lambda_choice, newx = x[test, ], type = 'class')
+
+#Confusion matrix
+ridge_conf_mx <- table(pred=ridge_predict, true=y[test])
+ridge_conf_mx
+error <- (ridge_conf_mx[2] + ridge_conf_mx[3])/length(ridge_predict)
+1-error
+```
+
+## LASSO
+
+```{r, cache=TRUE}
+#LASSO
+lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
+cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')
+
+#Lambda choice
+lasso_lam <- cv_lasso$lambda.min
+
+#Get predictions
+lasso_predict <- predict(lasso_fit, s = lasso_lam, newx = x[test, ], type = 'class')
+
+#Get coefficients
+lasso_coeff <- predict(lasso_fit, s = lasso_lam, type = 'coefficients')
+
+non_zero_lasso_coef <- lasso_coeff[lasso_coeff != 0]
+non_zero_lasso_coef
+#Confusion matrix
+lasso_mx <- table(pred=lasso_predict, true=y[test])
+lasso_mx
+error <- (lasso_mx[2] + lasso_mx[3])/length(lasso_predict)
+1-error
+```
+
+- Some of the non-zero coefficients include:
+- Pitch type
+- Count
+- Outs and Inning
+- Batter height
+- Whether the game is home or away
+- Where the pitch landed
 

### 2021-12-10 Slides.Rmd
Add to slides

@@
 knitr::opts_chunk$set(echo = FALSE)
+load("Data/usable_data.Rda")
 ```
@@
 - Catchers getting more strikes translates to more outs, and fewer runs for the opposing team
+- https://baseballsavant.mlb.com/sporty-videos?playId=273b22a4-f522-4009-87d1-14176772182d
 
@@
 ```{r cars, echo = FALSE, message = FALSE, cache=TRUE}
-load("Data/usable_data.Rda")
 x=c(-0.95,0.95,0.95,-0.95,-0.95)
@@
 
-```{r}
+```{r, cache=T}
 x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
@@
 
-```{r, cache=TRUE}
+```{r, cache=TRUE, message=FALSE}
 #LASSO
@@
 non_zero_lasso_coef <- lasso_coeff[lasso_coeff != 0]
-non_zero_lasso_coef
+
 #Confusion matrix
@@
 ```
+
+## Model Comparison
+
+- Boosting with interaction depth of 16, shrinkage of 0.1, and 500 trees has the highest accuracy
+
+```{r}
+df_rf %>%
+  rename(parameter = nodesize) %>%
+  bind_rows(final_df_gbm %>%
+              group_by(trees) %>%
+              summarize(accuracy = mean(accuracy)) %>%
+              arrange(desc(accuracy)) %>%
+              mutate(model = "boosting") %>%
+              select(model, accuracy, trees) %>%
+              rename(parameter = trees)) %>%
+  arrange(desc(accuracy))
+```
+
+## Results
+
+- To give credit to each catcher, we use this equation for every pitch:
+  - If strike: 1 - Strike Probability
+  - If ball: Strike Probability * -1

### 2021-12-10 Trees.R

@@ -178,8 +178,23 @@ final_df_gbm %>%
        y = "Accuracy",
        title = "Boosting Accuracy by # of Trees")
 
+final_df_gbm %>%
+  group_by(trees) %>%
+  summarize(accuracy = mean(accuracy)) %>%
+  arrange(desc(accuracy)) %>%
+  mutate(model = "boosting") %>%
+  select(model, accuracy, trees)
 
-
+df_rf %>%
+  rename(parameter = nodesize) %>%
+  bind_rows(final_df_gbm %>%
+              group_by(trees) %>%
+              summarize(accuracy = mean(accuracy)) %>%
+              arrange(desc(accuracy)) %>%
+              mutate(model = "boosting") %>%
+              select(model, accuracy, trees) %>%
+              rename(parameter = trees)) %>%
+  arrange(desc(accuracy))
 
 # Final model on the entire data set (351,891 rows)
 load("Final-Model/final_boosting_model.Rda")
@@ -232,6 +247,10 @@ data = data %>%
 data %>% filter(strike == 2, game_date != "2021-08-22") %>%
   select(game_date, count, inning, catcher_name, home_team, release_speed, strike_prob, strike) %>%
   arrange(strike_prob)
+
+
+
+
 
 
 

### 2021-12-10 Slides.Rmd
Fixed up

@@
 
-\tiny
 ```{r, echo=FALSE}
@@
 
-```{r, cache=T}
+```{r}
 x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
@@
 
-```{r, cache=TRUE, message=FALSE}
+```{r, message=FALSE}
 #LASSO

### 2021-12-10 Slides.Rmd
Commit

--- 2021-12-10 Slides.Rmd
@@
 
-```{r cars, echo = FALSE, message = FALSE, cache=TRUE}
+```{r, echo = FALSE, message = FALSE, cache=TRUE}
 x=c(-0.95,0.95,0.95,-0.95,-0.95)
@@
 ```{r, echo=FALSE}
-data_no_catchers <- usable_data[, -18]
-
-train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
-test <- (-train)
-
-log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
-
-pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
-pred[pred >= 0.5] <- 'strike'
-pred[pred < 0.5] <- 'ball'
-
-```
-
-```{r}
-conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
-error <- (conf_mx[2] + conf_mx[3])/length(pred)
+load("Model-Outputs/logistic-CM.Rda")
+load("Model-Outputs/logistic-error.Rda")
 
@@
 ```{r, cache=T}
+data_no_catchers <- usable_data[, -18]
 x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]

### 2021-12-10 Slides.Rmd

@@
 
-```{r, cache=T}
+```{r}
 data_no_catchers <- usable_data[, -18]
+
 x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]

### 2021-12-10 Slides.Rmd
Commit changes

@@
 
-```{r, echo=FALSE}
-load("Model-Outputs/logistic-CM.Rda")
-load("Model-Outputs/logistic-error.Rda")
+```{r, echo=FALSE, cache=TRUE}
+data_no_catchers <- usable_data[, -18]
+train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
+test <- (-train)
+log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
+pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
+pred[pred >= 0.5] <- 'strike'
+pred[pred < 0.5] <- 'ball'
+```
 
+```{r, cache=TRUE}
+conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
+error <- (conf_mx[2] + conf_mx[3])/length(pred)
 conf_mx
@@
 
-```{r}
+```{r, cache=TRUE}
 data_no_catchers <- usable_data[, -18]
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, cache=TRUE}
 #LASSO

### 2021-12-10 Slides.Rmd
Finish slides

@@
 library(randomForest)
+library(caret)
+library(knitr)
 knitr::opts_chunk$set(echo = FALSE)
@@
 - We used:
-- Pitch type and pitch release speed, position, and spin rate
+- Pitch type, pitch release speed, position, and spin rate
 - Whether or not the pitcher and batter are right or left handed
@@
   geom_point(aes(x = 16, y = 0.935), color = "red") +
-  labs(x = "Accuracy", y = "Interactin Depth",
+  labs(y = "Accuracy", x = "Interactin Depth",
        color = "Shrinkage",
@@
               rename(parameter = trees)) %>%
-  arrange(desc(accuracy))
+  arrange(desc(accuracy)) %>%
+  kable
+```
+
+## Variable Importance
+
+```{r, message=FALSE,echo=FALSE, cache = T, warning=FALSE}
+load("Final-Model/final_boosting_model.Rda")
+var = summary.gbm(final_model, plotit = F)
+ggplot(var, aes(x = fct_reorder(var, rel.inf), y = rel.inf, fill = rel.inf)) +
+  geom_col() +
+  coord_flip() +
+  labs(y = "Relative Influence",
+       title = "Predictor Variable Importance") +
+  theme_minimal()+
+  theme(axis.title.y = element_blank()) +
+  guides(fill = F)
 ```
@@
   - If ball: Strike Probability * -1
+
+```{r, fig.width=2, fig.height=2}
+# Analysis examples
+ggplot()+
+  geom_path(data = sz, aes(x = x, y = y)) +
+  xlim(-1.8, 1.8) +
+  ylim(0.5, 5) +
+  coord_equal() +
+  geom_point(aes(x = .5, y = 2.5)) +
+  geom_text(aes(x = 0.6, y = 2.8, label = "0.9")) +
+  geom_point(aes(x = -.5, y = 4)) +
+  geom_text(aes(x = -0.4, y = 4.3, label = "0.2")) +
+  theme_minimal()+
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank()) 
+```
+
+- If strike: 1 - 0.9 = 0.1 | 1 - 0.2 = 0.8
+- If ball: 0.9 * -1 = -0.9 | 0.2 * -1 = -0.2
+
+## Results
+
+\tiny
+```{r, cache= T, message=FALSE}
+load("Data/pitchData.Rda")
+# Analysis
+data = data %>%
+  mutate(strike_prob = predict(final_model, data, type = "response"),
+         strike = as.numeric(as.character(strike)))
+
+data = data %>%
+  mutate(credit = case_when(
+    strike == 1 ~ 1 - strike_prob,
+    strike == 0 ~ strike_prob * -1))
+```
+
+```{r}
+
+# Leader board
+data %>%
+  group_by(catcher_name) %>%
+  summarize(strikes_above_avg = sum(credit),
+            pitches_caught = n(),
+            strikes_aa_100 = strikes_above_avg / (pitches_caught / 100)) %>%
+  filter(pitches_caught > 2000) %>%
+  arrange(desc(strikes_above_avg)) %>% head(10) %>%
+  rename("Catcher Name" = catcher_name,
+         "Strikes Above Average" = strikes_above_avg,
+         "Pitches Caught" = pitches_caught,
+         "Strikes Above Average Per 100 Pitches Caught" = strikes_aa_100) %>% 
+  kable
+
+data %>%
+  group_by(catcher_name) %>%
+  summarize(strikes_above_avg = sum(credit),
+            pitches_caught = n(),
+            strikes_aa_100 = strikes_above_avg / (pitches_caught / 100)) %>%
+  filter(pitches_caught > 2000) %>%
+  arrange(strikes_above_avg) %>% head(10) %>%
+  rename("Catcher Name" = catcher_name,
+         "Strikes Above Average" = strikes_above_avg,
+         "Pitches Caught" = pitches_caught,
+         "Strikes Above Average Per 100 Pitches Caught" = strikes_aa_100) %>% 
+  kable
+```
+
+## Video Example 1
+
+- Strike (0.00108 strike probability)
+  - https://baseballsavant.mlb.com/sporty-videos?playId=2a91c3cf-e5d9-41f9-86e4-88700536a6de
+- Austin Nola gained his team 1 - 0.00108 = 0.9982 strikes from this pitch
+
+## Video Example 2
+
+- Ball (0.99087 strike probability)
+  - https://baseballsavant.mlb.com/sporty-videos?playId=3509cf12-7e2c-4beb-88af-d3b3cc736c02
+- Kevan Smith lost his team -0.99087 strikes from this pitch

### 2021-12-10 Trees.R

@@ -229,7 +229,9 @@ data %>%
             pitches_caught = n(),
             strikes_aa_100 = strikes_above_avg / (pitches_caught / 100)) %>%
   filter(pitches_caught > 2000) %>%
-  arrange(desc(strikes_above_avg))
+  arrange(desc(strikes_above_avg)) %>% head(20) %>%
+  rename("Catcher Name" = catcher_name)
+
 
 data %>%
   group_by(catcher_name) %>%
@@ -239,20 +241,53 @@ data %>%
   filter(n > 2000) %>%
   arrange(strikes_above_avg)
 
+# Catcher
+data %>%
+  filter(strike == 0) %>%
+  select(game_date, count, inning, catcher_name, home_team, release_speed, strike_prob) %>%
+  arrange(desc(strike_prob)) %>% data.frame() %>% head(10)
+
 # Find video examples
 data = data %>%
   mutate(strike_prob = predict(final_model, data, type = "response"),
          strike = as.numeric(as.character(strike)))
 
-data %>% filter(strike == 2, game_date != "2021-08-22") %>%
+data %>% filter(strike == 1, game_date != "2021-08-22") %>%
   select(game_date, count, inning, catcher_name, home_team, release_speed, strike_prob, strike) %>%
   arrange(strike_prob)
 
 
+# Analysis examples
+ggplot()+
+  geom_path(data = sz, aes(x = x, y = y)) +
+  xlim(-1.8, 1.8) +
+  ylim(0.5, 5) +
+  coord_equal() +
+  geom_point(aes(x = .5, y = 2.5)) +
+  geom_text(aes(x = 0.5, y = 2.9, label = "0.9")) +
+  geom_point(aes(x = -.5, y = 4)) +
+  geom_text(aes(x = -0.5, y = 4.4, label = "0.2")) +
+  labs(title = "Credit Example") +
+  theme_minimal()+
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank()) 
 
 
 
+var = summary.gbm(final_model, plotit = F)
+
+ggplot(var, aes(x = fct_reorder(var, rel.inf), y = rel.inf, fill = rel.inf)) +
+  geom_col() +
+  coord_flip() +
+  labs(y = "Relative Influence",
+       title = "Predictor Variable Importance") +
+  theme_minimal()+
+  theme(axis.title.y = element_blank()) +
+  guides(fill = F)
 
 
+  
 
 

### 2021-12-10 Trees.R
Commit

@@ -252,9 +252,9 @@ data = data %>%
   mutate(strike_prob = predict(final_model, data, type = "response"),
          strike = as.numeric(as.character(strike)))
 
-data %>% filter(strike == 1, game_date != "2021-08-22") %>%
+data %>% filter(strike == 0, game_date != "2021-08-22", catcher_name == "Salvador Perez") %>%
   select(game_date, count, inning, catcher_name, home_team, release_speed, strike_prob, strike) %>%
-  arrange(strike_prob)
+  arrange(desc(strike_prob))
 
 
 # Analysis examples

### 2021-12-13 Paper.Rmd
Started the motivation section of the paper

---
title: "Paper"
author: "Nathan Hemenway"
date: "12/13/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Motivation:
Catcher framing is the art of making a pitch look better than it really is. This is a skill a catcher can have to convince the umpire to call a pitch that would otherwise be called a strike a ball. If a pitch is for all intents and purposes a ball, then the batter likely will not swing at it. Then if the catcher can make it appear like a strike to the umpire, the umpire will call it a strike and bring the batter one step closer to an out. This is an obvious advantage, since the more strike outs take place, the less of opportunity the opposing team has to score runs while at-bat.

Our idea to measure this phenomenon is by using statistical machine learning methods in order to predict whether a given pitch is a strike. Given the nature of baseball, there will be pitches that are likely strikes and likely balls. If a catcher can convince the umpire to call a likely ball a strike, then that catcher is a good catcher and gets credited for that pitch. On the other hand, if the umpire calls what should have been a strike a ball, then the catcher did not do a good job and is penalized for the pitch. We sought to find out which catchers are best at pitch framing by predicting how likely the pitches thrown are to be strikes, and then seeing how well the catchers can turn them into strikes.

### 2021-12-14 Paper.Rmd
Changed wording
Add methodology section

@@
 ---
-title: "Paper"
-author: "Nathan Hemenway"
-date: "12/13/2021"
+title: "A Machine Learning Approach to MLB Catcher Framing"
+author: "Nathan Hemenway and Matthew Boyd"
+date: "12/16/2021"
 output: pdf_document
@@
 
+<style type="text/css">
+  body{
+  font-size: 12pt;
+}
+</style>
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(glmnet)
+library(gbm)
+library(randomForest)
+library(caret)
+library(knitr)
+knitr::opts_chunk$set(echo = FALSE)
+load("Data/usable_data.Rda")
+x=c(-0.95,0.95,0.95,-0.95,-0.95)
+y=c(1.5,1.5,3.5,3.5,1.5)
+sz=data.frame(x,y)
 ```
 
-Motivation:
+# Motivation
+
 Catcher framing is the art of making a pitch look better than it really is.
-This is a skill a catcher can have to convince the umpire to call a pitch that would otherwise be called a strike a ball.
+This is a skill a catcher can have to convince the umpire to call a pitch that would otherwise be called a ball, a strike.
 If a pitch is for all intents and purposes a ball, then the batter likely will not swing at it.
@@
 
-Our idea to measure this phenomenon is by using statistical machine learning methods in order to predict whether a given pitch is a strike.
+Our idea to measure this phenomenon is to use statistical machine learning methods in order to predict whether a given pitch is a strike.
 Given the nature of baseball, there will be pitches that are likely strikes and likely balls.
@@
 We sought to find out which catchers are best at pitch framing by predicting how likely the pitches thrown are to be strikes, and then seeing how well the catchers can turn them into strikes.
+
+# Methodology
+
+Our methodology is to use available data to predict whether a pitch will be a strike for all data points up until the catcher catches the ball.
+This will give us a good idea of whether any pitch, given a number of characteristics, will be called a strike or called a ball.
+From the model output, we can get a probability that every pitch will be a strike and compare that to the observed outcome of the pitch.
+From here we need to find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
+
+To give credit to each catcher, we use this equation for every pitch:
+
+ - If observed strike: 1 - Strike Probability  
+ - If observed ball: Strike Probability * -1
+
+To give an example, below is a plot of the strike zone.
+Umpires will try to make a call of a strike or ball if the pitch is located inside the rectangle.
+However, umpires don't have access to a strike zone while actually making calls themselves, so there will be some error as to whether a pitch an umpire calls a strike, is actually a strike (inside the strike zone).
+
+The point located inside the strike zone is a theoretical location of a pitch with a 0.9 strike probability.
+That's quite high but it makes sense, given the pitch is in the strike zone.
+The pitch outside of the strike zone has a 0.2 strike probability since the pitch lands outside the strike zone.
+If the pitch with a 0.9 strike probability gets called a strike, the catcher will earn 1 - 0.9 = 0.1 strikes worth of credit.
+This is a small contribution given that the pitch is more likely to be a strike anyway.
+However, if the pitch gets called a ball, he will lose 0.9 strikes worth of credit which is a significant loss.
+That is because the catcher could have could have presented the pitch to the umpire very poorly, and he deserves to be be given credit with losing a strike for his team.
+If we look at the pitch out of the zone, if that pitch is an observed called strike, the catcher will receive 1 - 0.2 = 0.8 strikes worth of credit.
+That's a big gain for the catcher's team because he turned a pitch, more likely going to be a ball, into a strike and he should be rewarded.
+If that pitch is an observed ball, he will only lose -0.2 strikes worth of credit.
+That's small because the pitch is likely to be a ball anyway.
+
+```{r, fig.width=2, fig.height=2}
+ggplot()+
+  geom_path(data = sz, aes(x = x, y = y)) +
+  xlim(-1.8, 1.8) +
+  ylim(0.5, 5) +
+  coord_equal() +
+  geom_point(aes(x = .5, y = 2.5)) +
+  geom_text(aes(x = 0.6, y = 2.8, label = "0.9")) +
+  geom_point(aes(x = -.5, y = 4)) +
+  geom_text(aes(x = -0.4, y = 4.3, label = "0.2")) +
+  theme_minimal()+
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank()) 
+```
+
+Once we have an accurate model this approach is completed for every pitch in th 2021 Major League Baseball season since we will have a strike probability and we will know the observed outcome of the pitch (called strike or ball).
+This way we can see which catcher's are better at presenting pitches to the umpire to benefit their team.
+
+## Data
+
+## Models
+
+### Logistic Regression
+
+### Ridge Regression
+
+### LASSO
+
+### Random Forest
+
+### Boosting
+
+# Results
+
+# Conclusion

### 2021-12-14 Paper.Rmd
Add data description

@@
 From the model output, we can get a probability that every pitch will be a strike and compare that to the observed outcome of the pitch.
-From here we need to find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
+From here we can find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
+
+## Data
+
+The data contains pitch characteristics for every pitch thrown during the 2021 Major League Baseball season.
+It was scraped from [Baseball Savant](https://baseballsavant.mlb.com/) using the [baseballr](https://billpetti.github.io/baseballr/) package.
+The scraped data contains ~700,000 rows with ~90 columns.
+We are only interested in pitches that were a called strike or a ball.
+This is because if the batter swung at a pitch, how the catcher presents the pitch doesn't matter.
+This left ~350,000 rows to model from.
+
+## Variables
+
+## Models
+
+We chose to predict whether a pitch is a strike on several models to find the model with the highest accuracy. The model chosen will be the model used on the results.
+
+### Logistic Regression
+
+### Ridge Regression
+
+### LASSO
+
+### Random Forest
+
+### Boosting
+
+# Results
 
@@
 
-## Data
-
-## Models
-
-### Logistic Regression
-
-### Ridge Regression
-
-### LASSO
-
-### Random Forest
-
-### Boosting
-
-# Results
-
 # Conclusion

### 2021-12-14 Paper.Rmd
Started working on logistic regression/ridge regression/LASSO models

--- 2021-12-14 Paper.Rmd
@@
 
-### Logistic Regression
+## Logistic Regression
 
-### Ridge Regression
+```{r}
+set.seed(445)
+load("~/DSCI 445 proj/project-7/Data/usable_data.Rda")
+data_no_catchers <- usable_data[, -18]
 
-### LASSO
+train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
+test <- (-train)
+
+log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
+summary(log_reg_fit)
+
+pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
+pred[pred >= 0.5] <- 'strike'
+pred[pred < 0.5] <- 'ball'
+
+conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
+error <- (conf_mx[2] + conf_mx[3])/length(pred)
+
+conf_mx
+1-error
+```
+
+We started with a logistic regression classifier using the selected variables as a preliminary model for predicting strikes.
+The model did not perform very impressively, with a prediction accuracy of 0.67.
+The summary for the logistic regression model gives which predictors are statistically significant, which included:
+- Pitch type, release speed, z release position
+- Whether the batter is a lefty/righty
+- Count
+- Where the pitch landed
+- Most of the innings
+- Batter height
+- Whether it was a home game
+
+## Ridge Regression and LASSO
+
+#Ridge Regression
+
+```{r}
+set.seed(445)
+library(glmnet)
+
+x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
+y <- data_no_catchers$strike
+
+lambda <- seq(0.001, 10, length=100)
+
+#Create training and test data set
+train <- sample(1:nrow(x), nrow(x)/2)
+test <- (-train)
+ridge_reg_fit <-  glmnet(x[train,], y[train], alpha = 0, lambda = lambda, family='binomial')
+
+#Choose lambda
+cv_ridge <- cv.glmnet(x[train, ], y[train], alpha=0, family='binomial')
+lambda_choice <- cv_ridge$lambda.min
+
+#Get predictions
+ridge_predict <- predict(ridge_reg_fit, s = lambda_choice, newx = x[test, ], type = 'class')
+
+#Confusion matrix
+ridge_conf_mx <- table(pred=ridge_predict, true=y[test])
+ridge_conf_mx
+error <- (ridge_conf_mx[2] + ridge_conf_mx[3])/length(ridge_predict)
+1-error
+```
+The ridge regression model performed modestly with a prediction accuracy of 0.672.
+This is hardly any different from the logistic regression model, so it also is not the best choice of model to be used to rank the catchers.
+
+#LASSO
 

### 2021-12-14 Paper.Rmd
Added more to LASSO

@@
 From the model output, we can get a probability that every pitch will be a strike and compare that to the observed outcome of the pitch.
-From here we need to find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
+From here we can find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
 
@@
 
+The data contains pitch characteristics for every pitch thrown during the 2021 Major League Baseball season.
+It was scraped from [Baseball Savant](https://baseballsavant.mlb.com/) using the [baseballr](https://billpetti.github.io/baseballr/) package.
+The scraped data contains ~700,000 rows with ~90 columns.
+We are only interested in pitches that were a called strike or a ball.
+This is because if the batter swung at a pitch, how the catcher presents the pitch doesn't matter.
+This left ~350,000 rows to model from.
+
+## Variables
+
 ## Models
+
+We chose to predict whether a pitch is a strike on several models to find the model with the highest accuracy. The model chosen will be the model used on the results.
 
@@
 
+```{r}
+set.seed(445)
+lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
+cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')
+
+#Lambda choice
+lasso_lam <- cv_lasso$lambda.min
+
+#Get predictions
+lasso_predict <- predict(lasso_fit, s = lasso_lam, newx = x[test, ], type = 'class')
+
+#Get coefficients
+lasso_coeff <- predict(lasso_fit, s = lasso_lam, type = 'coefficients')
+lasso_coeff
+
+non_zero_lasso_coef <- lasso_coeff[lasso_coeff != 0]
+#Confusion matrix
+lasso_mx <- table(pred=lasso_predict, true=y[test])
+lasso_mx
+error <- (lasso_mx[2] + lasso_mx[3])/length(lasso_predict)
+1-error
+```
+
+The model obtained using the LASSO gave a similar prediction accuracy as the logistic and ridge regression models at 0.673.
+The LASSO also performs variable selection, and gave non-zero coefficients for:
+- Pitch type
+- Count
+- Outs and Inning
+- Batter height
+- Whether the game is home or away
+- Where the pitch landed
+
 ### Random Forest

### 2021-12-15 Paper.Rmd
Move section to results
Add majority of the remaining parts of the paper

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, cache=T, echo=FALSE}
 library(tidyverse)
@@
 
-To give credit to each catcher, we use this equation for every pitch:
-
- - If observed strike: 1 - Strike Probability  
- - If observed ball: Strike Probability * -1
-
-To give an example, below is a plot of the strike zone.
-Umpires will try to make a call of a strike or ball if the pitch is located inside the rectangle.
-However, umpires don't have access to a strike zone while actually making calls themselves, so there will be some error as to whether a pitch an umpire calls a strike, is actually a strike (inside the strike zone).
-
-The point located inside the strike zone is a theoretical location of a pitch with a 0.9 strike probability.
-That's quite high but it makes sense, given the pitch is in the strike zone.
-The pitch outside of the strike zone has a 0.2 strike probability since the pitch lands outside the strike zone.
-If the pitch with a 0.9 strike probability gets called a strike, the catcher will earn 1 - 0.9 = 0.1 strikes worth of credit.
-This is a small contribution given that the pitch is more likely to be a strike anyway.
-However, if the pitch gets called a ball, he will lose 0.9 strikes worth of credit which is a significant loss.
-That is because the catcher could have could have presented the pitch to the umpire very poorly, and he deserves to be be given credit with losing a strike for his team.
-If we look at the pitch out of the zone, if that pitch is an observed called strike, the catcher will receive 1 - 0.2 = 0.8 strikes worth of credit.
-That's a big gain for the catcher's team because he turned a pitch, more likely going to be a ball, into a strike and he should be rewarded.
-If that pitch is an observed ball, he will only lose -0.2 strikes worth of credit.
-That's small because the pitch is likely to be a ball anyway.
-
-```{r, fig.width=2, fig.height=2}
-ggplot()+
-  geom_path(data = sz, aes(x = x, y = y)) +
-  xlim(-1.8, 1.8) +
-  ylim(0.5, 5) +
-  coord_equal() +
-  geom_point(aes(x = .5, y = 2.5)) +
-  geom_text(aes(x = 0.6, y = 2.8, label = "0.9")) +
-  geom_point(aes(x = -.5, y = 4)) +
-  geom_text(aes(x = -0.4, y = 4.3, label = "0.2")) +
-  theme_minimal()+
-  theme(axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.y = element_blank(),
-        axis.text.y = element_blank()) 
-```
-
-Once we have an accurate model this approach is completed for every pitch in th 2021 Major League Baseball season since we will have a strike probability and we will know the observed outcome of the pitch (called strike or ball).
-This way we can see which catcher's are better at presenting pitches to the umpire to benefit their team.
-
 ## Data
@@
 
-## Models
+Of the 93 variables to choose from, we chose the ones listed below.
+The reason we chose these variables was because we thought they could all have an impact on whether a pitch will be a called strike or not.
+  - Pitch type, pitch release speed, release position, and spin rate  
+  - Whether or not the pitcher and batter are right or left handed  
+  - Count, number of outs during the at-bat, and inning number  
+  - Where the pitch landed  
+  - Whether the game was played home or away  
+  - How tall the batter is
+
+Several variables in the data set also contained mostly NA values and those columns were ignored in modeling.
+
+# Models
 
@@
 
-## Logistic Regression
+### Logistic Regression
 
-```{r}
+```{r, cache = T, warning=FALSE, message=FALSE, echo=FALSE}
 set.seed(445)
-load("~/DSCI 445 proj/project-7/Data/usable_data.Rda")
+load("Data/usable_data.Rda")
 data_no_catchers <- usable_data[, -18]
@@
 
-## Ridge Regression and LASSO
+### Ridge Regression
 
-#Ridge Regression
-
-```{r}
+```{r, cache=TRUE, warning=FALSE, message=FALSE, echo=FALSE}
 set.seed(445)
@@
 
-#LASSO
+### LASSO
 
-```{r}
+```{r, cache=TRUE, warning=FALSE, message=FALSE, echo=FALSE}
 set.seed(445)
@@
 
+The next step for modeling involved fitting the data on tree type model.
+The first model tested was random forest.
+With the same variables used above, we fit a random forest model on the data with a nodesize of 10, 30, 50, 70, and 90.
+We kept the number of trees the same at 500.
+After each model was fit, we took the out-of-bag error rate and compared the models to find the most accurate.
+More values for nodesize would have been considered but each model took a long time to run.
+Running these 5 models took about 64 minutes total.
+
+```{r, echo=FALSE, fig.width=7, fig.height=4, cache=TRUE}
+load("Data/pitchData.Rda")
+load("Model-Outputs/random-forest.Rda")
+
+ggplot(df_rf, aes(x = nodesize, y = accuracy))+
+  geom_line() +
+  geom_point() +
+  geom_point(data = df_rf %>% 
+               filter(accuracy == max(accuracy)), aes(x = nodesize, y = accuracy), color = "red") +
+  ylim(0.925, 0.935) +
+  labs(x = "Nodesize",
+       y = "Accuracy",
+       title = "Random Forest OOB Accuracy by Nodesize") +
+  theme_minimal()
+```
+
+As you can see from the image, the random forest model with a nodesize of 10 had the highest OOB accuracy.
+One thing to note is how much more accurate the random forest models performed than logistic regression, ridge regression, and LASSO.
+This shows how powerful growing several trees are on prediction rate.
+
 ### Boosting
+
+A similar process was performed for boosting with a few adjustments.
+Instead of using the OOB error, we performed 3-fold cross validation to tune parameters on interaction depth and shrinkage.
+The reason  we only chose 3-fold cross validation was because the models would take a long time to run.
+We tested interaction depth's of 6, 11, and 16 with shrinkage of 0.1, 0.01, 0.001.
+The number of trees was set to 500 for all models.
+This process performed 27 models which took over 5 hours to run.
+Once all models were finished, we compared the cross validation accuracy with the plot below.
+
+```{r, echo=FALSE, fig.width=6, fig.height=2.5, warning=FALSE, message=FALSE}
+library(tidyverse)
+load("Model-Outputs/boosting.Rda")
+
+ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
+  geom_line() +
+  theme_minimal()+
+  geom_point() +
+  geom_point(aes(x = 16, y = 0.935), color = "red") +
+  labs(y = "Accuracy", x = "Interactin Depth",
+       color = "Shrinkage",
+       title = "Boosting Accuracy by Interaction Depth and Shrinkage")
+```
+
+The model that performed best had a interaction depth of 16 with shrinkage rate of 0.1.
+Now that we have the best model, it's now time to again perform 3-fold cross validation on the number of trees.
+We tested trees of 300, 600, 900, and 1200 with shrinkage of 0.1 and interaction depth of 16.
+Below show the results of the cross validation accuracy by number of trees.
+
+```{r,  fig.width=6, fig.height=3.2, echo=FALSE, message=FALSE, warning=FALSE}
+load("Model-Outputs/boosting2.Rda")
+final_df_gbm %>%
+  group_by(trees) %>%
+  summarize(accuracy = mean(accuracy)) %>%
+  arrange(desc(accuracy)) %>%
+  ggplot(aes(x = trees, y = accuracy)) +
+  geom_line(color = "goldenrod") +
+  theme_minimal() +
+  labs(x = "Number of Trees",
+       y = "Accuracy",
+       title = "Boosting Accuracy by # of Trees")
+```
+
+500 trees was used in the initial 3-fold cross validation and it shows the highest accuracy among all boosting models.
+
+### Model Comparison
+
+We now compare all tree methods used to find the model with the highest accuracy.
+These models all performed at a much higher accuracy rate than logistic regression, ridge regression, and LASSO.
+Below are all the models sorted by highest accuracy.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+library(knitr)
+df_rf %>%
+  rename(parameter = nodesize) %>%
+  bind_rows(final_df_gbm %>%
+              group_by(trees) %>%
+              summarize(accuracy = mean(accuracy)) %>%
+              arrange(desc(accuracy)) %>%
+              mutate(model = "boosting") %>%
+              select(model, accuracy, trees) %>%
+              rename(parameter = trees)) %>%
+  arrange(desc(accuracy)) %>%
+  kable
+```
+
+As you can see, boosting with shrinkage rate of 0.1, interaction depth of 16, and 500 trees performed the best with a 93.5%. This model will be used on the results.
+
+### Variable Importance
+
+```{r, message=FALSE,echo=FALSE, warning=FALSE}
+library(gbm)
+load("Final-Model/final_boosting_model.Rda")
+var = summary.gbm(final_model, plotit = F)
+ggplot(var, aes(x = fct_reorder(var, rel.inf), y = rel.inf, fill = rel.inf)) +
+  geom_col() +
+  coord_flip() +
+  labs(y = "Relative Influence",
+       title = "Predictor Variable Importance") +
+  theme_minimal()+
+  theme(axis.title.y = element_blank()) +
+  guides(fill = F)
+```
+
+Looking at the variable importance for whether a pitch will be a strike on the best model, the location of the pitch is the most important (plate_x and plate_z) with the count of the pitch and height of th batter (sz_top and sz_bot).
+Most variables have very little importance compared to the location of the pitch.
+The handedness of the pitcher (righty/lefty) and the location (home/away) have the lowest importance of all variables.
 
@@
 
+To give credit to each catcher, we use this equation for every pitch:
+
+ - If observed strike: 1 - Strike Probability  
+ - If observed ball: Strike Probability * -1
+
+To give an example, below is a plot of the strike zone.
+Umpires will try to make a call of a strike or ball if the pitch is located inside the rectangle.
+However, umpires don't have access to a strike zone while actually making calls themselves, so there will be some error as to whether a pitch an umpire calls a strike, is actually a strike (inside the strike zone).
+
+The point located inside the strike zone is a theoretical location of a pitch with a 0.9 strike probability.
+That's quite high but it makes sense, given the pitch is in the strike zone.
+The pitch outside of the strike zone has a 0.2 strike probability since the pitch lands outside the strike zone.
+If the pitch with a 0.9 strike probability gets called a strike, the catcher will earn 1 - 0.9 = 0.1 strikes worth of credit.
+This is a small contribution given that the pitch is more likely to be a strike anyway.
+However, if the pitch gets called a ball, he will lose 0.9 strikes worth of credit which is a significant loss.
+That is because the catcher could have could have presented the pitch to the umpire very poorly, and he deserves to be be given credit with losing a strike for his team.
+If we look at the pitch out of the zone, if that pitch is an observed called strike, the catcher will receive 1 - 0.2 = 0.8 strikes worth of credit.
+That's a big gain for the catcher's team because he turned a pitch, more likely going to be a ball, into a strike and he should be rewarded.
+If that pitch is an observed ball, he will only lose -0.2 strikes worth of credit.
+That's small because the pitch is likely to be a ball anyway.
+
+```{r, fig.width=2, fig.height=2, cache=TRUE, echo=FALSE}
+ggplot()+
+  geom_path(data = sz, aes(x = x, y = y)) +
+  xlim(-1.8, 1.8) +
+  ylim(0.5, 5) +
+  coord_equal() +
+  geom_point(aes(x = .5, y = 2.5)) +
+  geom_text(aes(x = 0.6, y = 2.8, label = "0.9")) +
+  geom_point(aes(x = -.5, y = 4)) +
+  geom_text(aes(x = -0.4, y = 4.3, label = "0.2")) +
+  theme_minimal()+
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank()) 
+```
+
+This approach is completed for every pitch in th 2021 Major League Baseball season since we will have a strike probability and we will know the observed outcome of the pitch (called strike or ball).
+This way we can see which catcher's are better at presenting pitches to the umpire to benefit their team.
+
+```{r, message=FALSE, echo=FALSE}
+load("Data/pitchData.Rda")
+# Analysis
+data = data %>%
+  mutate(strike_prob = predict(final_model, data, type = "response"),
+         strike = as.numeric(as.character(strike)))
+
+data = data %>%
+  mutate(credit = case_when(
+    strike == 1 ~ 1 - strike_prob,
+    strike == 0 ~ strike_prob * -1))
+```
+
+```{r, echo=FALSE}
+# Leader board
+data %>%
+  group_by(catcher_name) %>%
+  summarize(strikes_above_avg = sum(credit),
+            pitches_caught = n(),
+            strikes_aa_100 = strikes_above_avg / (pitches_caught / 100)) %>%
+  filter(pitches_caught > 2000) %>%
+  arrange(desc(strikes_above_avg)) %>% head(10) %>%
+  rename("Catcher Name" = catcher_name,
+         "Strikes Above Average" = strikes_above_avg,
+         "Pitches Caught" = pitches_caught,
+         "Strikes Above Average Per 100 Pitches Caught" = strikes_aa_100) %>% 
+  kable
+
+data %>%
+  group_by(catcher_name) %>%
+  summarize(strikes_above_avg = sum(credit),
+            pitches_caught = n(),
+            strikes_aa_100 = strikes_above_avg / (pitches_caught / 100)) %>%
+  filter(pitches_caught > 2000) %>%
+  arrange(strikes_above_avg) %>% head(10) %>%
+  rename("Catcher Name" = catcher_name,
+         "Strikes Above Average" = strikes_above_avg,
+         "Pitches Caught" = pitches_caught,
+         "Strikes Above Average Per 100 Pitches Caught" = strikes_aa_100) %>% 
+  kable
+```
+
+The tables above show the top 10 framing catchers and the bottom 10 framing catchers.
+The top three include Max Stassi of the Los Angeles Angels, Jose Trevino of the Texas Rangers, and J.T.
+Realmuto of the Philidephia.
+The bottom three include Salvador Perez of the Kansas City Royals, Pedro Severino of the Baltimore Orioles, and Zack Collins of the Chicago White Sox.
+To interpret this, Max Stassi gained his team 99.2 strikes above average just from how he presents the ball to the umpire.
+Salvador Perez lost his team 102.6 strikes below average from how he presents the ball to the umpire.
+That's a difference of about 200 strikes between the bottom and top, a large difference.
+
 # Conclusion
+
+How catchers catch the ball seems unimportant to the naked eye.
+An umpire is supposed to call a strike if the pitch location is within a certain range but since umpires are human, they can be wrong.
+Our analysis shows that some catcher's add value to their team from the small skill of how they catch the ball.
+The next time you watch a baseball game, just know that how a catcher catches the ball can have a greater impact on the game than anyone would think.
+
+# References

### 2021-12-16 Paper.Rmd
Add references section

@@
 # References
+
+A. Liaw and M. Wiener (2002). Classification and Regression by randomForest. R News 2(3), 18--22
+
+“Baseball Savant: Trending MLB Players, Statcast and Visualizations.” Baseballsavant.com,
+    https://baseballsavant.mlb.com/.
+
+“Catcher Framing: Glossary.” MLB.com, https://www.mlb.com/glossary/statcast/catcher-framing.
+
+Bill Petti (2021). baseballr: Functions for Acquiring and Analyzing Baseball Data.
+  https://billpetti.github.io/baseballr/, https://github.com/BillPetti/baseballr/.
+
+Brandon Greenwell, Bradley Boehmke, Jay Cunningham and GBM Developers (2020). gbm: Generalized Boosted
+  Regression Models. R package version 2.1.8. https://CRAN.R-project.org/package=gbm
+
+Jerome Friedman, Trevor Hastie, Robert Tibshirani (2010). Regularization Paths for Generalized Linear
+  Models via Coordinate Descent. Journal of Statistical Software, 33(1), 1-22. URL
+  https://www.jstatsoft.org/v33/i01/.
+
+Max Kuhn (2021). caret: Classification and Regression Training. R package version 6.0-90.
+  https://CRAN.R-project.org/package=caret
+
+Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
+  https://doi.org/10.21105/joss.01686
+
+Yihui Xie (2021). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version
+  1.36.

### 2021-12-16 Paper.Rmd
Fixed a mistake
Commit but don't push
First round of proofreading

@@
 This is a skill a catcher can have to convince the umpire to call a pitch that would otherwise be called a ball, a strike.
-If a pitch is for all intents and purposes a ball, then the batter likely will not swing at it.
+If a pitch is for all intents and purposes a ball, then the batter will likely not swing at it.
 Then if the catcher can make it appear like a strike to the umpire, the umpire will call it a strike and bring the batter one step closer to an out.
-This is an obvious advantage, since the more strike outs take place, the less of opportunity the opposing team has to score runs while at-bat.
+This is an obvious advantage, since the more strike outs take place, the less opportunity the opposing team has to score runs while at-bat.
 
@@
 Given the nature of baseball, there will be pitches that are likely strikes and likely balls.
-If a catcher can convince the umpire to call a likely ball a strike, then that catcher is a good catcher and gets credited for that pitch.
-On the other hand, if the umpire calls what should have been a strike a ball, then the catcher did not do a good job and is penalized for the pitch.
-We sought to find out which catchers are best at pitch framing by predicting how likely the pitches thrown are to be strikes, and then seeing how well the catchers can turn them into strikes.
+If a catcher can convince the umpire to call a likely ball a strike, then that catcher is a good at catcher framing.
+On the other hand, if the umpire calls what should have been a strike a ball, then the catcher did a poor job at catcher framing.
+We sought to find out which catchers are best at catcher framing by predicting how likely the pitches are to be strikes, and then seeing how well the catchers can turn them into strikes.
+We wanted to see who was best at catcher framing in the 2021 season.
 
@@
 
-Our methodology is to use available data to predict whether a pitch will be a strike for all data points up until the catcher catches the ball.
-This will give us a good idea of whether any pitch, given a number of characteristics, will be called a strike or called a ball.
-From the model output, we can get a probability that every pitch will be a strike and compare that to the observed outcome of the pitch.
-From here we can find out which catchers during the 2021 season excelled at getting more called strikes than their probabilities say they would.
+Our methodology is to use available data to predict the probability a pitch will be called a strike.
+We can compare this probability to the decision made by the umpire to assess how well the catcher performed catcher framing.
+If a low probability of strike pitch was called a strike, we give the catcher a 'credit' of 1 - p(strike), and vice versa for if it is called a ball.
+We will run this procedure for all of the pitches grouped by each catcher.
+From here we can find out which catchers during the 2021 season excelled at catcher framing, by comparing how much credit they got overall.
 
@@
 This is because if the batter swung at a pitch, how the catcher presents the pitch doesn't matter.
+Also, we are not interested in pitches where the batter hit the ball.
 This left ~350,000 rows to model from.
@@
 
-Several variables in the data set also contained mostly NA values and those columns were ignored in modeling.
+Several variables in the data set also contained mostly NA values and those columns were not used in modeling.
 
@@
 
-We chose to predict whether a pitch is a strike on several models to find the model with the highest accuracy. The model chosen will be the model used on the results.
+We chose to predict whether a pitch is a strike on several preliminary models to find the model with the highest prediction accuracy. The model chosen will be the model used to find the results.
 
@@
 The first model tested was random forest.
-With the same variables used above, we fit a random forest model on the data with a nodesize of 10, 30, 50, 70, and 90.
-We kept the number of trees the same at 500.
-After each model was fit, we took the out-of-bag error rate and compared the models to find the most accurate.
-More values for nodesize would have been considered but each model took a long time to run.
+With the same variables used above, we fit a random forest model on the data with nodesizes of 10, 30, 50, 70, and 90.
+We kept the number of trees constant at 500.
+After each model was fit, we took the out-of-bag error rate and compared the models to find the most accurate model.
+More values for nodesize would have been considered, but each model took a long time to run.
 Running these 5 models took about 64 minutes total.
@@
 
-As you can see from the image, the random forest model with a nodesize of 10 had the highest OOB accuracy.
+As you can see from the image, the random forest model with a nodesize of 10 had the highest out-of-bag accuracy.
 One thing to note is how much more accurate the random forest models performed than logistic regression, ridge regression, and LASSO.
-This shows how powerful growing several trees are on prediction rate.
+This shows how powerful growing several trees are on prediction accuracy.
 
@@
 
-A similar process was performed for boosting with a few adjustments.
-Instead of using the OOB error, we performed 3-fold cross validation to tune parameters on interaction depth and shrinkage.
-The reason  we only chose 3-fold cross validation was because the models would take a long time to run.
-We tested interaction depth's of 6, 11, and 16 with shrinkage of 0.1, 0.01, 0.001.
+A similar process was performed for boosting, but with a few adjustments.
+Instead of using the out-of-bag error, we performed 3-fold cross validation to tune parameters on interaction depth and shrinkage.
+The reason we only chose 3-fold cross validation was because the models took a long time to run.
+We tested interaction depths of 6, 11, and 16, with shrinkage of 0.1, 0.01, 0.001.
 The number of trees was set to 500 for all models.
@@
 
-The model that performed best had a interaction depth of 16 with shrinkage rate of 0.1.
-Now that we have the best model, it's now time to again perform 3-fold cross validation on the number of trees.
+The model that performed best had a interaction depth of 16 with a shrinkage rate of 0.1.
+Now that we have the best model, it is now time to again perform 3-fold cross validation on the number of trees.
 We tested trees of 300, 600, 900, and 1200 with shrinkage of 0.1 and interaction depth of 16.
-Below show the results of the cross validation accuracy by number of trees.
+The results of the cross validation accuracy by number of trees are shown below.
 
@@
 
-500 trees was used in the initial 3-fold cross validation and it shows the highest accuracy among all boosting models.
+500 trees were used in the initial 3-fold cross validation and it shows the highest accuracy among all boosting models.
 
@@
 
-As you can see, boosting with shrinkage rate of 0.1, interaction depth of 16, and 500 trees performed the best with a 93.5%. This model will be used on the results.
+As you can see, boosting with shrinkage rate of 0.1, interaction depth of 16, and 500 trees performed the best with a 93.5% prediction accuracy.
+This model will be used to find results of how the catchers rank for the skill of catcher framing.
 
@@
 
-Looking at the variable importance for whether a pitch will be a strike on the best model, the location of the pitch is the most important (plate_x and plate_z) with the count of the pitch and height of th batter (sz_top and sz_bot).
+Looking at the variable importance for whether a pitch will be a strike on the best model, the location of the pitch is the most important (plate_x and plate_z), and also the count of the pitch and height of the batter (sz_top and sz_bot).
 Most variables have very little importance compared to the location of the pitch.
@@
 
- - If observed strike: 1 - Strike Probability  
- - If observed ball: Strike Probability * -1
+ - If called a strike: 1 - Strike Probability  
+ - If called a ball: Strike Probability * -1
 
 To give an example, below is a plot of the strike zone.
-Umpires will try to make a call of a strike or ball if the pitch is located inside the rectangle.
-However, umpires don't have access to a strike zone while actually making calls themselves, so there will be some error as to whether a pitch an umpire calls a strike, is actually a strike (inside the strike zone).
+Umpires will try to make a call of a strike or ball if the pitch is located inside the rectangle (strike zone).
+However, umpires do not have access to a strike zone while actually making calls, so there will be some error as to whether a pitch an umpire calls a strike is actually a strike (inside the strike zone).
 
-The point located inside the strike zone is a theoretical location of a pitch with a 0.9 strike probability.
-That's quite high but it makes sense, given the pitch is in the strike zone.
-The pitch outside of the strike zone has a 0.2 strike probability since the pitch lands outside the strike zone.
-If the pitch with a 0.9 strike probability gets called a strike, the catcher will earn 1 - 0.9 = 0.1 strikes worth of credit.
-This is a small contribution given that the pitch is more likely to be a strike anyway.
+The point located inside the strike zone is a theoretical location of a pitch with a probability of 0.9 of being a strike.
+This makes sense, since the pitch is in the strike zone.
+The pitch outside of the strike zone has a probability of 0.2 of being called a strike, since the pitch lands outside the strike zone.
+If the pitch with a probability of 0.9 of being a strike gets called a strike, the catcher will earn 1 - 0.9 = 0.1 worth of credit towards a strike.
+This is a small contribution since the pitch is likely a strike anyway.
 However, if the pitch gets called a ball, he will lose 0.9 strikes worth of credit which is a significant loss.
-That is because the catcher could have could have presented the pitch to the umpire very poorly, and he deserves to be be given credit with losing a strike for his team.
-If we look at the pitch out of the zone, if that pitch is an observed called strike, the catcher will receive 1 - 0.2 = 0.8 strikes worth of credit.
-That's a big gain for the catcher's team because he turned a pitch, more likely going to be a ball, into a strike and he should be rewarded.
-If that pitch is an observed ball, he will only lose -0.2 strikes worth of credit.
-That's small because the pitch is likely to be a ball anyway.
+This is because the catcher could have presented the pitch to the umpire very poorly, and deserves to be be deducted credit for losing a strike for his team.
+If we look at the pitch out of the zone, if that pitch is called a strike, the catcher will receive 1 - 0.2 = 0.8 strikes worth of credit.
+That is a big gain for the catcher's team because he turned a likely ball into a strike and should be rewarded.
+If that pitch is a called a ball, he will only lose -0.2 strikes worth of credit.
+That is small because the pitch is likely to be a ball anyway.
 
@@
 
-This approach is completed for every pitch in th 2021 Major League Baseball season since we will have a strike probability and we will know the observed outcome of the pitch (called strike or ball).
-This way we can see which catcher's are better at presenting pitches to the umpire to benefit their team.
+This approach is completed for every pitch in the 2021 Major League Baseball season since we will have a strike probability and we will know the observed outcome of the pitches (called strike or ball).
+This way we can see which catchers are better at catcher framing for the benefit of their team.
 
@@
 
-The tables above show the top 10 framing catchers and the bottom 10 framing catchers.
+The tables above show the top 10 and bottom 10 catchers in terms of catcher framing ability.
 The top three include Max Stassi of the Los Angeles Angels, Jose Trevino of the Texas Rangers, and J.T.
-Realmuto of the Philidephia.
+Realmuto of the Philidelphia Phillies.
 The bottom three include Salvador Perez of the Kansas City Royals, Pedro Severino of the Baltimore Orioles, and Zack Collins of the Chicago White Sox.
@@
 That's a difference of about 200 strikes between the bottom and top, a large difference.
+We felt it was more important to analyze the gross amount of credit a catcher earns, instead of average per pitch, since this leaves out catchers with very few pitches thrown to them.
 
@@
 How catchers catch the ball seems unimportant to the naked eye.
-An umpire is supposed to call a strike if the pitch location is within a certain range but since umpires are human, they can be wrong.
-Our analysis shows that some catcher's add value to their team from the small skill of how they catch the ball.
+An umpire is supposed to call a strike if the pitch location is within the strike zone, but since umpires are human, they can be wrong.
+Our analysis shows that some catchers add value to their team from the skill of how they catch the ball.
 The next time you watch a baseball game, just know that how a catcher catches the ball can have a greater impact on the game than anyone would think.

### 2021-12-16 Paper.Rmd
Final adjustments to code and paper

@@
 We can compare this probability to the decision made by the umpire to assess how well the catcher performed catcher framing.
-If a low probability of strike pitch was called a strike, we give the catcher a 'credit' of 1 - p(strike), and vice versa for if it is called a ball.
+If a low probability of strike pitch was called a strike, the catcher gets rewarded, and vice versa for if it is called a ball.
+The details of how this is performed are in the Results section below.
 We will run this procedure for all of the pitches grouped by each catcher.
-From here we can find out which catchers during the 2021 season excelled at catcher framing, by comparing how much credit they got overall.
+From here we can find out which catchers during the 2021 season excelled at catcher framing.
 
@@
 
-The next step for modeling involved fitting the data on tree type model.
+The next step for modeling involved fitting the data on tree type models.
 The first model tested was random forest.

### 2021-12-16 Cleaning.R

@@ -1,9 +1,10 @@
+#setup
+devtools::install_github(repo = "BillPetti/baseballr")
+
 # Load libraries
 library(tidyverse)
 library(baseballr)
 
-#setup
-# devtools::install_github(repo = "BillPetti/baseballr")
 
 # data description
 # https://baseballsavant.mlb.com/csv-docs

### 2021-12-16 Trees.R

@@ -40,8 +40,8 @@ for(i in seq(10, 90, 20)) {
 }
 proc.time() - time
 
-# save(df_rf, file = "Model-Outputs/random-forest.Rda")
-load("Model-Outputs/random-forest.Rda")
+save(df_rf, file = "Model-Outputs/random-forest.Rda")
+# load("Model-Outputs/random-forest.Rda")
 
 ggplot(df_rf, aes(x = nodesize, y = accuracy))+
   geom_line() +
@@ -53,11 +53,6 @@ ggplot(df_rf, aes(x = nodesize, y = accuracy))+
        y = "Accuracy",
        title = "Random Forest OOB Accuracy by Nodesize") +
   theme_minimal()
-
-
-varImp(model_rf) %>% 
-  arrange(desc(Overall))
-
 
 
 # Boosting
@@ -104,7 +99,9 @@ df_gbm_final = df_gbm %>%
   summarize(accuracy = mean(accuracy)) %>%
   arrange(desc(accuracy))
 
-load("Model-Outputs/boosting.Rda")
+
+save(df_gbm_final, file = "Model-Outputs/boosting.Rda")
+# load("Model-Outputs/boosting.Rda")
 
 ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
   geom_line() +
@@ -116,7 +113,7 @@ ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.charact
        y = "Boosting Accuracy by Interaction Depth and Shrinkage")
 
 
- # save(df_gbm_final, file = "Model-Outputs/boosting.Rda")
+
 
 
 # Boosting with interaction depth of 16 and lambda of 0.1
@@ -157,15 +154,15 @@ total_time2 = proc.time() - time
 
 
 # Add boosting with 500 trees
-load("Model-Outputs/boosting2.Rda")
-
 final_df_gbm = final_df_gbm %>% 
   bind_rows(df_gbm %>%
               filter(interaction_depth == 16, lambda == 0.1) %>%
               mutate(trees = 500) %>%
               select(model, accuracy, trees))
 
-# save(final_df_gbm, file = "Model-Outputs/boosting2.Rda")
+save(final_df_gbm, file = "Model-Outputs/boosting2.Rda")
+# load("Model-Outputs/boosting2.Rda")
+
 
 final_df_gbm %>%
[…]

### 2021-12-16 Paper.Rmd
Commit final touches to paper

@@
 ```{r, echo=FALSE, fig.width=7, fig.height=4, cache=TRUE}
+
 load("Data/pitchData.Rda")
@@
 ```{r, echo=FALSE, fig.width=6, fig.height=2.5, warning=FALSE, message=FALSE}
+
 library(tidyverse)
@@
 ```{r,  fig.width=6, fig.height=3.2, echo=FALSE, message=FALSE, warning=FALSE}
+
 load("Model-Outputs/boosting2.Rda")
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
 library(knitr)
@@
 ```{r, message=FALSE,echo=FALSE, warning=FALSE}
+
 library(gbm)
@@
 ```{r, fig.width=2, fig.height=2, cache=TRUE, echo=FALSE}
+
 ggplot()+
@@
 ```{r, message=FALSE, echo=FALSE}
+
 load("Data/pitchData.Rda")
@@
 ```{r, echo=FALSE}
+
 # Leader board
